Identification of high-yielding soybean lines with exceptional seed composition qualities

### 2022-04-08 doc/manuscript/manuscript.Rmd
Worked on a couple of functions in the sandbox directory to make some nicer looking summary tables. Also rearranged the packages file a little bit to keep categories of packages together.

These thirty lines were then grouped into two new tests of 15 RILs each which were then grown in both the 2020 and 2021 seasons. Thesew tests were grown in CLA and CAS in 2020 and CAS and PLY in 2021.

>>>>

These thirty lines were then grouped into two new tests of 15 RILs each which were then grown in both the 2020 and 2021 seasons. These tests were grown in CLA and CAS in 2020 and CAS and PLY in 2021.

## Statistical Analysis
The data for seed yield, seed oil, and seed protein contents were analyzed using a mixed model with the metan[@r_metan] R package. Environment, replication nested with environment, and the interaction of genotype with environment were considered to be random effects while genotype was considered to be a fixed effect.

### 2022-04-08 doc/manuscript/manuscript.tex
Worked on a couple of functions in the sandbox directory to make some nicer looking summary tables. Also rearranged the packages file a little bit to keep categories of packages together.

These thirty lines were then grouped into two new tests of 15 RILs each
which were then grown in both the 2020 and 2021 seasons. Thesew tests
were grown in CLA and CAS in 2020 and CAS and PLY in 2021.

>>>>

These thirty lines were then grouped into two new tests of 15 RILs each
which were then grown in both the 2020 and 2021 seasons. These tests
were grown in CLA and CAS in 2020 and CAS and PLY in 2021.

\hypertarget{statistical-analysis}{%
\subsection{Statistical Analysis}\label{statistical-analysis}}

The data for seed yield, seed oil, and seed protein contents were
analyzed using a mixed model with the metan\citep{r_metan} R package.
Environment, replication nested with environment, and the interaction of
genotype with environment were considered to be random effects while
genotype was considered to be a fixed effect.
